### 2016-01-14 number_theory/hw/hw1.tex
working on number theory homework

@@

\item Suppose $a,b\in\ZZ$ with $b\neq 0$ and $a|b$. Prove that $|a| \leq |b|$.
\end{enumerate}
\end{document}

>>>>

\usepackage{cancel}

@@

\item Suppose $a,b\in\ZZ$ with $b\neq 0$ and $a|b$. Prove that $|a| \leq |b|$.
\begin{quote}
Since $a|b$, we have that $b=an$ for some $n\in\ZZ$. We first need to show that $n \neq 0$.
Since $b\neq 0$, $an\neq 0$. Therefore both $a$ and $n$ must not be equal to 0. If we apply
the absolute value to $b$, we have that $|b| = |an|$. We know that $|an| = |a||n|$. Since
$n\neq 0$, $|n| \geq 1$. We also know that $|a| \geq 1$, since $a\neq 0$. Therefore
$|a||n| \geq |a|$, or $|an| \geq |a|$. Since $|b| = |an|$, we have that $|a|\leq|b|$.
\end{quote}
$\triangle$

\item Suppose that $a,b,c,d\in\ZZ$ are such that $a|b$ and $c|d$. Does $a+c$ necessarily
divide $b+d$?
\begin{quote}
Assume $a+c$ divides $b+d$. Let $a=1$ and $c=-1$. Both 1 and -1 divide all elements of $\ZZ$, but
$1 + -1 = 0$, and 0 does not divide anything. Therefore by counterexample it does not.
\end{quote}
$\triangle$

\item Suppose that $b\in\ZZ$.
\begin{enumerate}
\item If $4|b^{2}$, prove that $2|b$.
\begin{quote}
Assume that $4|b^{2}$ but $2\cancel{|}b$. Then $b = 2n + r$ for some $n$ and $r$ in $\ZZ$. We know
that $r\neq 0$, and that $0 < r < 2$. Therefore $r = 1$. If we square both sides, we get
\begin{align*}
b^{2} &= (2n+1)^{2}\\
&= 4n^{2}+4n+1\\
&= 4(n^{2} + n) + 1.
\end{align*}
Therefore $4\cancel{|}b$, since it has a remainder of 1.
\end{quote}

\end{enumerate}
\end{enumerate}
\end{document}
